### 2011-06-02 docs/pubs/EIM-2011/intro.tex
resolve section references from intro.tex to other .tex files

The rest of this paper is organized as follows. \secref{sec-framework}
briefly describes the various components used within our
approach. \secref{sec-annotation} describes the extensions we have
developed for Morpho and Metacat to support semantic
annotation. \secref{sec-applications} describes the types of data
discovery queries and integration services supported by our
framework. \secref{sec-related} briefly describes related work, and we
summarize our contributions in \secref{sec-summary}.

>>>>

The rest of this paper is organized as follows. \secref{sec:annotation}
briefly describes the various components used within our
approach. \secref{sec:framework} describes the extensions we have
developed for Morpho and Metacat to support semantic
annotation. \secref{sec:application} describes the types of data
discovery queries and integration services supported by our
framework. \secref{sec:related} briefly describes related work, and we
summarize our contributions in \secref{sec:summary}.
